---
title: 'MOT ADHD: Accuracy analysis'
author: "Ben Cowley (adapted from Sami Karadeniz)"
output:
  html_document:
    theme: readable
    toc: yes
    toc_depth: 4
    toc_float:
      collapsed: yes
  pdf_document:
    toc: yes
    toc_depth: '4'
---

# Setup

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
# Load libraries
#library(Rmisc)
# library(gghalves)
# library(kableExtra)
# library(knitr)
library(forcats)
library(here)
library(ez)
library(retimes)
library(afex)
library(multcomp)
library(emmeans)
library(sjPlot)
library(patchwork)
library(tidyverse)
source('znbnz_utils.R')

#         THIS SCRIPT IS CREATED USING DUMMY DATA, SO ID IS CODED AS ID_MOT AT SOME PLACEs
datpth <- file.path(here(), "data")

# Path to demographics excel-file.
demographics_path <- file.path(datpth, "subjects_log.xlsx")

# Path to the folder containing trials data in csv-format.
trials_path <- file.path(datpth, "trials_trim")

# Path to figure output folder
SAVE <- FALSE
odir <- file.path(here(), "Figures")

# Define the theme of the plots as a variable.
plot_theme <- "theme_minimal"
DIAGNOSTICS <- TRUE
PLOTS <- TRUE
```


```{r load_data, include = FALSE, warning = FALSE}
# Load data import functions.
source("functions/import_trials_data_csv.r")

# Load demographics data.
demographics <- readxl::read_xlsx(demographics_path)

# Load trials data.
trials_data <- import_trials_data(trials_path)
```


```{r recode_variables, include = FALSE, warning = FALSE}
# Re-code variables: demographics.
# demographics$Subj = demographics$ID
demographics$ID_MOT <- as.factor(sprintf('%02d', demographics$ID_MOT))
demographics$ID <- as.factor(demographics$ID)

# Re-code variables: trials data.
trials_data$ID = as.factor(trials_data$ID)
trials_data$Group = as.factor(trials_data$Group)
trials_data$Group <- relevel(trials_data$Group, "Control")
trials_data$Task = as.factor(trials_data$Task)
trials_data$Distractors = as.factor(trials_data$Distractors)
trials_data$TrialType = as.factor(trials_data$TrialType)
trials_data$Hemifield = as.factor(trials_data$Hemifield)
trials_data$Visibility = as.factor(trials_data$Visibility)
trials_data$PhotoD = as.factor(trials_data$PhotoD)
trials_data$Resp = as.factor(trials_data$Resp)
trials_data$Blink = as.factor(trials_data$Blink)
```


# Preprocessing

## Pruning

__Discarding subjects before preprocessing__. First, we use the following criteria for choosing the subjects to bepreprocessed in the first place:

* subjects have been measured with the photodetector
* subjects have the full number of usable sets (= 4)
* subjects do not have too many trial-rejections

__Trimming trials by RT__: to ensure accuracy features cannot include any misclassified trials, we trim trials outside 200 -- 900 ms. These thresholds are based on the stimulus presentation duration times two (200ms), plus the shortest ISI of 700ms (200+700 = 900ms). We'll keep RT == 0 trials since they are catch trials or misses.

```{r discard_by_photod-sets, warning = FALSE}
analysis_trials <- demographics %>% 
  filter(Valid_for_analysis == TRUE) %>%
  mutate("dom_resp" = Handedness == Response_hand) %>%
  select(ID, dom_resp) %>% 
  inner_join(trials_data, by = "ID")
 analysis_trials$ID = as.factor(analysis_trials$ID)

levels(analysis_trials$Resp)[1] <- "Hit"
levels(analysis_trials$Resp)[2] <- "False Alarm"

trials_ok <- analysis_trials

if (PLOTS){
# Reaction time scatter plot.
trials_ok %>%
  ggplot(aes(x = ID, y = RT, color = TrialType)) +
    geom_jitter(aes(alpha = 0.2)) +
    xlab("Subject") +  
    ylab("Reaction time (s)") +
    ggtitle("Reaction time distribution, valid subjects, trimmed trials") +
    get(plot_theme)() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
}
```



```{r Setup_contrasts}
grid.lvls <- expand.grid(Task = c('AttendFull', 'AttendLeft', 'AttendRight'),
                      Distractors = c('Absent', 'Present'),
                      Group = c('ADHD', 'Control'))

con_FvLR_adhd <- rbind("contrast" = c(0,0.5,0,0.5,0,-0.25,0,-0.25,0,-0.25,0,-0.25))
con_LvFR_adhd <- rbind("contrast" = c(0,-0.25,0,-0.25,0,0.5,0,0.5,0,-0.25,0,-0.25))
con_RvFL_adhd <- rbind("contrast" = c(0,-0.25,0,-0.25,0,-0.25,0,-0.25,0,0.5,0,0.5))
con_dstr_adhd <- rbind("contrast" = c(0,1/3,0,-1/3,0,1/3,0,-1/3,0,1/3,0,-1/3))
con_drAF_adhd <- contrasts21(con_FvLR_adhd * con_dstr_adhd)
con_drAL_adhd <- contrasts21(con_LvFR_adhd * con_dstr_adhd)
con_drAR_adhd <- contrasts21(con_RvFL_adhd * con_dstr_adhd)

con_FvLR_ctrl <- rbind("contrast" = c(0.5,0,0.5,0,-0.25,0,-0.25,0,-0.25,0,-0.25,0))
con_LvFR_ctrl <- rbind("contrast" = c(-0.25,0,-0.25,0,0.5,0,0.5,0,-0.25,0,-0.25,0))
con_RvFL_ctrl <- rbind("contrast" = c(-0.25,0,-0.25,0,-0.25,0,-0.25,0,0.5,0,0.5,0))
con_dstr_ctrl <- rbind("contrast" = c(1/3,0,-1/3,0,1/3,0,-1/3,0,1/3,0,-1/3,0))
con_drAF_ctrl <- contrasts21(con_FvLR_ctrl * con_dstr_ctrl)
con_drAL_ctrl <- contrasts21(con_LvFR_ctrl * con_dstr_ctrl)
con_drAR_ctrl <- contrasts21(con_RvFL_ctrl * con_dstr_ctrl)

con_drAF_CvA <- contrasts21(con_drAF_adhd * -1 + con_drAF_ctrl)
con_drAL_CvA <- contrasts21(con_drAL_adhd * -1 + con_drAL_ctrl)
con_drAR_CvA <- contrasts21(con_drAR_adhd * -1 + con_drAR_ctrl)
```



# Results
Results are given for each **task** x **distractor state** combination at the
group and single subject levels. We will look at:

Accuracy

* hit rates
* false alarm rates
* distractor effects*

*Distractor effects are calculated in the following way:

$$\frac{HR_{distractors \ absent} - HR_{distractors \ present}}
{HR_{distractors \ absent} + HR_{distractors \ present}}$$


```{r calculate_behav_data, warning = FALSE}
# We'll create one data frame for each behavioral performance measure.

# Hit rates.
trials_ok %>%
  filter(TrialType == "Real") %>%
  group_by(ID, dom_resp, Group, Task, Distractors) %>%
  summarise(n_trials = n(),
            hit_rate = sum(Resp == "Hit") / n_trials) -> 
hit_rates
hit_rates$Task <- droplevels(hit_rates$Task, exclude = "AttendNone")
# hit_rates$sq_hr <- hit_rates$hit_rate ^ 2


# False alarms.
trials_ok %>%
  filter(TrialType == "Catch", Task != "AttendFull") %>%
  group_by(ID, dom_resp, Group, Task, Distractors) %>%
  summarise(n_trials = n(),
            fa_rate = sum(Resp == "False Alarm") / n_trials) -> 
fa_rates
fa_rates$Task <- droplevels(fa_rates$Task, exclude = "AttendFull")
# fa_rates$sq_far <- fa_rates$fa_rate ^ 2


# Distractor effect.
hit_rates %>%
  select(-n_trials) %>%
  spread(key = "Distractors", value = "hit_rate") %>%
  mutate(distractor_effect = (Absent - Present) / (Absent + Present)) %>%
  select(-Absent, -Present) -> 
distractor_effect
distractor_effect$Task <- droplevels(distractor_effect$Task, exclude = "AttendNone")
# distractor_effect$log_de <- log(distractor_effect$distractor_effect)


if (PLOTS){
  # Normality test and visualise distros
  qqnorm(hit_rates$hit_rate, main = "Hit rates deviations Normal Q-Q Plot")
  qqline(hit_rates$hit_rate)

  line.xy <- hit_rates %>%
  group_by(Group, Distractors, Task) %>%
  summarize(xpt = median(hit_rate), ypt = max(density(hit_rate)$y))
  
  plot.hr <- hit_rates %>%
    ggplot(aes(hit_rate, fill=Group, colour=Group)) +
      geom_density(alpha=.3) +
      scale_x_continuous(n.breaks = 3) +
      scale_y_continuous(n.breaks = 3) +
      geom_rug(aes(color = Group, linetype = Group), length = unit(0.05, "npc")) +
      geom_segment(data = line.xy, aes(x = xpt, y = ypt / 2, xend = xpt, yend = ypt + 1, color = Group, linetype = Group), size = 1) +
      facet_grid(Task~Distractors, scales = "free_y") +
      labs(title = "hit rate") + xlab(NULL) +
      get(plot_theme)() +
      theme(strip.text.y = element_blank()) 
# hit_rates %>%
#   ggplot(aes(hit_rate, fill=Task)) +
#   geom_density(alpha=.4) +
#   facet_wrap(Group~Distractors, ncol=2) +
#   get(plot_theme)()
}

if (PLOTS){
  # Normality test and visualise distros
  qqnorm(fa_rates$fa_rate, main = "False Alarm rates deviations Normal Q-Q Plot")
  qqline(fa_rates$fa_rate)
  
  line.xy <- fa_rates %>%
  group_by(Group, Distractors, Task) %>%
  summarize(xpt = median(fa_rate), ypt = max(density(fa_rate)$y))
    
  plot.fa <- fa_rates %>%
    ggplot(aes(fa_rate, fill=Group, colour=Group)) +
      geom_density(alpha=.3) +
      scale_x_continuous(n.breaks = 3) +
      scale_y_continuous(n.breaks = 3) +
      geom_rug(aes(color = Group, linetype = Group), length = unit(0.05, "npc")) +
      geom_segment(data = line.xy, aes(x = xpt, y = ypt / 2, xend = xpt, yend = ypt + 1, color = Group, linetype = Group), size = 1) +
      facet_grid(Task~Distractors, scales = "free_y") +
      labs(title = "false-alarm rate") + xlab(NULL) + ylab(NULL) +
      get(plot_theme)() +
      theme(strip.text.y = element_blank()) 
# fa_rates %>%
#   ggplot(aes(fa_rate, fill=Task)) +
#   geom_density(alpha=.4) +
#   facet_wrap(Group~Distractors, ncol=2) +
#   get(plot_theme)()
}
if (PLOTS){
  # Normality test and visualise distros
  qqnorm(distractor_effect$distractor_effect, main = "distractor_effect deviations Normal Q-Q Plot")
  qqline(distractor_effect$distractor_effect)
  
  line.xy <- distractor_effect %>%
  group_by(Group, Task) %>%
  summarize(xpt = median(distractor_effect), ypt = max(density(distractor_effect)$y))
  
  plot.de <- distractor_effect %>%
    ggplot(aes(distractor_effect, fill=Group, colour=Group)) +
      geom_density(alpha=.3) +
      scale_y_continuous(n.breaks = 3) +
      geom_rug(aes(color = Group, linetype = Group), length = unit(0.05, "npc")) +
      geom_segment(data = line.xy, aes(x = xpt, y = ypt / 2, xend = xpt, yend = ypt + 1, color = Group, linetype = Group), size = 1) +
      facet_wrap(~Task, scales = "free_y", ncol = 1, strip.position = "right") +
      labs(title = "distractor effect") + xlab(NULL) + ylab(NULL) +
      get(plot_theme)() +
      theme(strip.text.y = element_text(size = rel(1.2)))
# distractor_effect %>%
#   ggplot(aes(distractor_effect, fill=Task)) +
#   geom_density(alpha=.4) +
#   facet_wrap(~Group, ncol=2) +
#   get(plot_theme)()
}

(plot.hr + plot.fa + plot.de) + plot_layout(guides="collect")
if (SAVE){
  ggsave(file.path(odir, "Accuracy.svg"), width = 11, height = 5)
}


```


## Hit rates

```{r hit_rates, warning = FALSE, fig.align = "center"}
if (PLOTS){
# Hit rates, group level.
hit_rates %>%
  ggplot(aes(x = Distractors, y = hit_rate, linetype = Group, color = Group)) +
    geom_boxplot(outlier.alpha = 0, alpha = 1/5) +
    geom_point(position = position_jitterdodge(jitter.width = 0.2)) +
    # geom_half_violin(draw_quantiles = c(0.25, 0.5, 0.75), alpha = 0) +
    scale_y_continuous(labels = scales::percent) +
    facet_wrap(~Task) +
    xlab("Distractor state") +
    ylab("Hit rate") +
    ggtitle("Hit rates, all task conditions, group level") +
    get(plot_theme)()
if (SAVE)
  ggsave(file.path(odir, "HITS.svg"))

}
if (PLOTS){
# Hit rates, group level, barchart with SEM.
p_dodge <- position_dodge(width = 0.9)

hit_rates %>%
  group_by(Group, Task, Distractors) %>%
  summarise(HR_mean = mean(hit_rate), HR_sem = sd(hit_rate)/sqrt(n())) %>%
  ggplot(aes(x = Distractors, y = HR_mean, fill = Group)) +
    geom_col(position = p_dodge) +
    geom_errorbar(aes(ymin = HR_mean - HR_sem, ymax = HR_mean + HR_sem),
                  position = p_dodge, width = 0.25) +
    scale_y_continuous(labels = scales::percent) +
    facet_wrap(~Task) +
    xlab("Distractor state") +
    ylab("Hit rate") +
    ggtitle("Hit rates, all task conditions, group level, +/- SEM") +
    scale_fill_brewer(palette = "Greys") +
    get(plot_theme)()

}
if (PLOTS){
# Hit rates, single subject.
hit_rates %>%
  ggplot(aes(x = Distractors, y = hit_rate, color = dom_resp)) +
    geom_line(aes(group = ID)) +
    geom_point() +
    scale_y_continuous(labels = scales::percent) +
    facet_grid(Group ~ Task) +
    xlab("Distractor state") +
    ylab("Hit rate") +
    ggtitle("Hit rates, all task conditions, single subject (color = response hand dominant)") +
    get(plot_theme)() +
    theme(legend.position = "none")
}

# Does response hand counter-balancing in CONTROL group affect hit rates?
ks.test(filter(hit_rates, Group == "Control" & !dom_resp)$hit_rate,
         filter(hit_rates, Group == "Control" & dom_resp)$hit_rate)
```

### Statistics for hit rates

```{r hit_rates_stats, warning = FALSE, fig.align = "center"}
# Mixed 3-way ANOVA.
hr_stats <- ezANOVA(hit_rates, dv = .(hit_rate),
                    wid = .(ID),
                    within = .(Task, Distractors),
                    between = .(Group),
                    type = 3, detailed = FALSE, return_aov = TRUE)
if (DIAGNOSTICS){
  ezanova_residuals <- purrr::map(hr_stats$aov, residuals)
  ezanova_residuals_tbl <- enframe(ezanova_residuals) %>% unnest
  hist(ezanova_residuals_tbl$value)
  shapiro.test(ezanova_residuals_tbl$value)
  print(hr_stats)
}

# Hit rate by lmer
hr_lmer <- lmer(hit_rate ~ Group*Distractors*Task + (1|Distractors:ID) + (1|Task:ID) + (1|ID), data = hit_rates)
if (DIAGNOSTICS){
  summary(hr_lmer)
  plot_model(hr_lmer, type = "diag")[[4]]
}
```

### Constrasts for Hit Rates

__Hit rate by LMM - joint tests and facet line plot of interactions__

```{r hit_rates_CONTRAST, warning = FALSE, fig.align = "center"}

joint_tests(hr_lmer)
joint_tests(hr_lmer, by = "Group")
joint_tests(hr_lmer, by = c("Distractors", "Task"))
joint_tests(hr_lmer, by = "Distractors")
joint_tests(hr_lmer, by = c("Task", "Group"))
joint_tests(hr_lmer, by = "Task")
joint_tests(hr_lmer, by = c("Distractors", "Group"))

cbind(grid.lvls, hr = predict(hr_lmer, newdata = grid.lvls, re.form=NA)) %>%
  ggplot(aes(Distractors, hr, linetype=Task)) + geom_point() +
  geom_line(aes(group=Task),size=1) +
  facet_wrap(~Group) + theme_bw() + ggtitle("HR values") + ylab("Hit Rate")
# cbind(grid.lvls, hr = predict(hr_lmer, newdata = grid.lvls, re.form=NA)) %>%
#   ggplot(aes(Distractors, hr, linetype=Group)) + geom_point() +
#   geom_line(aes(group=Group),size=1) +
#   facet_wrap(~Task) + theme_bw() + ggtitle("HR values") + ylab("Hit Rate")

```


__Contrasts performed on the LMM of spread levels (all x all interaction)__
```{r}
# Contrasts
hit_rates$Group <- relevel(hit_rates$Group, ref = "Control")
hit_rates$all_factors <- with(hit_rates, interaction(Group, Distractors, Task))
hr_contr <- lmer(hit_rate ~ all_factors + (1|ID), data = hit_rates)
# summary(hr_contr)

levels(hit_rates$all_factors)

# "main effect" of task within ADHD
cat("TEST CONTRAST: FvLR_adhd", con_FvLR_adhd)
summary(glht(hr_contr, linfct = mcp(all_factors = con_FvLR_adhd)), test = Ftest())
cat("TEST CONTRAST: LvFR_adhd", con_LvFR_adhd)
summary(glht(hr_contr, linfct = mcp(all_factors = con_LvFR_adhd)), test = Ftest())
cat("TEST CONTRAST: RvFL_adhd", con_RvFL_adhd)
summary(glht(hr_contr, linfct = mcp(all_factors = con_RvFL_adhd)), test = Ftest())

# "main effect" of distractor within ADHD
cat("TEST CONTRAST: dstr_adhd", con_dstr_adhd)
summary(glht(hr_contr, linfct = mcp(all_factors = con_dstr_adhd)), test = Ftest())

# Interaction of distractor and task levels in ADHD
cat("TEST CONTRAST: drAF_adhd", con_drAF_adhd)
summary(glht(hr_contr, linfct = mcp(all_factors = con_drAF_adhd)), test = Ftest())
cat("TEST CONTRAST: drAL_adhd", con_drAL_adhd)
summary(glht(hr_contr, linfct = mcp(all_factors = con_drAL_adhd)), test = Ftest())
cat("TEST CONTRAST: drAR_adhd", con_drAR_adhd)
summary(glht(hr_contr, linfct = mcp(all_factors = con_drAR_adhd)), test = Ftest())

# "main effect" of task within CTRL
cat("TEST CONTRAST: FvLR_ctrl", con_FvLR_ctrl)
summary(glht(hr_contr, linfct = mcp(all_factors = con_FvLR_ctrl)), test = Ftest())
cat("TEST CONTRAST: LvFR_ctrl", con_LvFR_ctrl)
summary(glht(hr_contr, linfct = mcp(all_factors = con_LvFR_ctrl)), test = Ftest())
cat("TEST CONTRAST: RvFL_ctrl", con_RvFL_ctrl)
summary(glht(hr_contr, linfct = mcp(all_factors = con_RvFL_ctrl)), test = Ftest())

# "main effect" of distractor within CTRL
cat("TEST CONTRAST: dstr_ctrl", con_dstr_ctrl)
summary(glht(hr_contr, linfct = mcp(all_factors = con_dstr_ctrl)), test = Ftest())

# Interaction of distractor and task levels in CTRL
cat("TEST CONTRAST: drAF_ctrl", con_drAF_ctrl)
summary(glht(hr_contr, linfct = mcp(all_factors = con_drAF_ctrl)), test = Ftest())
cat("TEST CONTRAST: drAL_ctrl", con_drAL_ctrl)
summary(glht(hr_contr, linfct = mcp(all_factors = con_drAL_ctrl)), test = Ftest())
cat("TEST CONTRAST: drAR_ctrl", con_drAR_ctrl)
summary(glht(hr_contr, linfct = mcp(all_factors = con_drAR_ctrl)), test = Ftest())

# Interaction of distractor and task levels between ADHD & CTRL
cat("TEST CONTRAST: drAF_ctrl V ADHD", con_drAF_CvA)
summary(glht(hr_contr, linfct = mcp(all_factors = con_drAF_CvA)), test = Ftest())
cat("TEST CONTRAST: drAL_ctrl V ADHD", con_drAL_CvA)
summary(glht(hr_contr, linfct = mcp(all_factors = con_drAL_CvA)), test = Ftest())
cat("TEST CONTRAST: drAR_ctrl V ADHD", con_drAR_CvA)
summary(glht(hr_contr, linfct = mcp(all_factors = con_drAR_CvA)), test = Ftest())

# # The PALOMÄKI APPROACH
# main_effect_GRUP <- rbind("Main effect CTRLvADHD" = c(1,-1,1,-1,1,-1,1,-1,1,-1,1,-1))
# main_effect_DSTR <- rbind("Main effect of Distractor" = c(-1,-1,1,1,-1,-1,1,1,-1,-1,1,1))
# full_vs_left <- rbind("Attend FULL vs LEFT" = c(1,1,1,1,-1,-1,-1,-1,0,0,0,0))
# full_vs_right <- rbind("Attend FULL vs RIGHT" = c(1,1,1,1,0,0,0,0,-1,-1,-1,-1))
#
# #Create matrix contrast for the MAIN EFFEFCT of "TASK":
# main_effect_TASK <- rbind(full_vs_left, full_vs_right)
#
# #take the PRODUCT of the main effect contrasts as a matrix
# interaction_DSTR.TASK <- rbind(main_effect_DSTR*full_vs_left,
#                                main_effect_DSTR*full_vs_right)
# interaction_GRUP.DSTR.TASK <- rbind(main_effect_GRUP*main_effect_DSTR*full_vs_left,
#                                     main_effect_GRUP*main_effect_DSTR*full_vs_right)
#
# #Perform contrast analyses. Compare the output against the original type-3 SS table of the 2x3 ANOVA. The numbers are identical.
# #MAIN EFFECT OF GROUP:
# summary(glht(hr_contr, linfct = mcp(all_factors = contrasts21(main_effect_GRUP))))
# #MAIN EFFECT OF DISTRACTOR:
# summary(glht(hr_contr, linfct = mcp(all_factors = contrasts21(main_effect_DSTR))))
# #MAIN EFFECT OF TASK:
# summary(glht(hr_contr, linfct = mcp(all_factors = contrasts21(main_effect_TASK))))
# #INTERACTION DISTRACTOR*TASK:
# summary(glht(hr_contr, linfct = mcp(all_factors = contrasts21(interaction_DSTR.TASK))))
# #INTERACTION GROUP*DISTRACTOR*TASK:
# summary(glht(hr_contr, linfct = mcp(all_factors = contrasts21(interaction_GRUP.DSTR.TASK))))
```



## False alarms

```{r fa_rates, warning = FALSE, fig.align = "center"}
if (PLOTS){
# False alarm rates, group level.
fa_rates %>%
  ggplot(aes(x = Distractors, y = fa_rate, linetype = Group, color = Group)) +
    geom_boxplot(outlier.alpha = 0, alpha = 1/5) +
    geom_point(position = position_jitterdodge(jitter.width = 0.2)) +
    # geom_half_violin(draw_quantiles = c(0.25, 0.5, 0.75), alpha = 0) +
    scale_y_continuous(labels = scales::percent) +
    facet_wrap(~Task) +
    xlab("Distractor state") +
    ylab("False alarm rate") +
    ggtitle("False alarm rates, all task conditions, group level") +
    get(plot_theme)()
if (SAVE)
  ggsave(file.path(odir, "FArate.svg"))

}
if (PLOTS){
# False alarm rates, group level, barchart with SEM.
p_dodge <- position_dodge(width = 0.9)

fa_rates %>%
  group_by(Group, Task, Distractors) %>%
  summarise(FA_mean = mean(fa_rate), FA_sem = sd(fa_rate)/sqrt(n())) %>%
  ggplot(aes(x = Distractors, y = FA_mean, fill = Group)) +
    geom_col(position = p_dodge) +
    geom_errorbar(aes(ymin = FA_mean - FA_sem, ymax = FA_mean + FA_sem),
                  position = p_dodge, width = 0.25) +
    scale_y_continuous(labels = scales::percent) +
    facet_wrap(~Task) +
    xlab("Distractor state") +
    ylab("False alarm rate") +
    ggtitle("False alarm rates, all task conditions, group level, +/- SEM") +
    scale_fill_brewer(palette = "Greys") +
    get(plot_theme)()

}
if (PLOTS){
# False alarm rates, single subject.
fa_rates %>%
  ggplot(aes(x = Distractors, y = fa_rate, color = dom_resp)) +
    geom_line(aes(group = ID)) +
    geom_point() +
    scale_y_continuous(labels = scales::percent) +
    facet_grid(Group ~ Task) +
    xlab("Distractor state") +
    ylab("False alarm rate") +
    ggtitle("False alarm rates, all task conditions, single subject") +
    get(plot_theme)() +
    theme(legend.position = "none")
}

# Does response hand counter-balancing in CONTROL group affect FA rates?
ks.test(filter(fa_rates, Group == "Control" & !dom_resp)$fa_rate,
         filter(fa_rates, Group == "Control" & dom_resp)$fa_rate)
```

### Statistics for false alarm rates:

```{r fa_rates_stats, warning = FALSE, fig.align = "center"}
# Mixed 3-way ANOVA.
fa_stats <- ezANOVA(fa_rates, dv = .(fa_rate),
                    wid = .(ID),
                    within = .(Task, Distractors),
                    between = .(Group),
                    type = 3, detailed = FALSE, return_aov = TRUE)
if (DIAGNOSTICS){
  ezanova_residuals <- purrr::map(fa_stats$aov, residuals)
  ezanova_residuals_tbl <- enframe(ezanova_residuals) %>% unnest
  hist(ezanova_residuals_tbl$value)
  shapiro.test(ezanova_residuals_tbl$value)
  print(fa_stats)
}

# False Alarm by lmer
fa_lmer <- lmer(fa_rate ~ Group*Distractors*Task + (1|Distractors:ID) + (1|Task:ID) + (1|ID), data = fa_rates)
if (DIAGNOSTICS){
  summary(fa_lmer)
  plot_model(fa_lmer, type = "diag")[[4]]
}
```


### Constrasts for False Alarms

__False Alarm by LMM - joint tests and facet line plot of interactions__

```{r false_alarm_CONTRAST, warning = FALSE, fig.align = "center"}

joint_tests(fa_lmer)
joint_tests(fa_lmer, by = "Group")
joint_tests(fa_lmer, by = c("Distractors", "Task"))
joint_tests(fa_lmer, by = "Distractors")
joint_tests(fa_lmer, by = c("Task", "Group"))
joint_tests(fa_lmer, by = "Task")
joint_tests(fa_lmer, by = c("Distractors", "Group"))

fa.grid.lvls <- expand.grid(Task = c('AttendLeft', 'AttendNone', 'AttendRight'),
                      Distractors = c('Absent', 'Present'),
                      Group = c('ADHD', 'Control'))

cbind(fa.grid.lvls, fa = predict(fa_lmer, newdata = fa.grid.lvls, re.form=NA)) %>%
  ggplot(aes(Distractors, fa, linetype=Task)) + geom_point() +
  geom_line(aes(group=Task),size=1) +
  facet_wrap(~Group) + theme_bw() + ggtitle("False Alarms") + ylab("False Alarms")
# cbind(fa.grid.lvls, fa = predict(fa_lmer, newdata = fa.grid.lvls, re.form=NA)) %>%
#   ggplot(aes(Distractors, fa, linetype=Group)) + geom_point() +
#   geom_line(aes(group=Group),size=1) +
#   facet_wrap(~Task) + theme_bw() + ggtitle("False Alarms") + ylab("False Alarms")

```


__Contrasts performed on the LMM of spread levels (all x all interaction)__
```{r}
# Contrasts
fa_rates$Group <- relevel(fa_rates$Group, ref = "Control")
fa_rates$all_factors <- with(fa_rates, interaction(Group, Distractors, Task))
fa_contr <- lmer(fa_rate ~ all_factors + (1|ID), data = fa_rates)
# summary(fa_contr)

levels(fa_rates$all_factors)

con_NvLR_adhd <- rbind("NvLR_adhd" = c(0,-0.25,0,-0.25,0,0.5,0,0.5,0,-0.25,0,-0.25))
con_LvNR_adhd <- rbind("LvNR_adhd" = c(0,0.5,0,0.5,0,-0.25,0,-0.25,0,-0.25,0,-0.25))
con_RvNL_adhd <- rbind("RvNL_adhd" = c(0,-0.25,0,-0.25,0,-0.25,0,-0.25,0,0.5,0,0.5))
con_dstr_adhd <- rbind("dstr_adhd" = c(0,1/3,0,-1/3,0,1/3,0,-1/3,0,1/3,0,-1/3))
con_drAN_adhd <- rbind("drAN_adhd" = contrasts21(con_NvLR_adhd * con_dstr_adhd))
con_drAL_adhd <- rbind("drAL_adhd" = contrasts21(con_LvNR_adhd * con_dstr_adhd))
con_drAR_adhd <- rbind("drAR_adhd" = contrasts21(con_RvNL_adhd * con_dstr_adhd))

con_NvLR_ctrl <- rbind("NvLR_ctrl" = c(-0.25,0,-0.25,0,0.5,0,0.5,0,-0.25,0,-0.25,0))
con_LvNR_ctrl <- rbind("LvNR_ctrl" = c(0.5,0,0.5,0,-0.25,0,-0.25,0,-0.25,0,-0.25,0))
con_RvNL_ctrl <- rbind("RvNL_ctrl" = c(-0.25,0,-0.25,0,-0.25,0,-0.25,0,0.5,0,0.5,0))
con_dstr_ctrl <- rbind("dstr_ctrl" = c(1/3,0,-1/3,0,1/3,0,-1/3,0,1/3,0,-1/3,0))
con_drAN_ctrl <- rbind("drAN_ctrl" = contrasts21(con_NvLR_ctrl * con_dstr_ctrl))
con_drAL_ctrl <- rbind("drAL_ctrl" = contrasts21(con_LvNR_ctrl * con_dstr_ctrl))
con_drAR_ctrl <- rbind("drAR_ctrl" = contrasts21(con_RvNL_ctrl * con_dstr_ctrl))

con_drAN_CvA <- rbind("drAN_CvA" = contrasts21(con_drAN_adhd * -1 + con_drAN_ctrl))
con_drAL_CvA <- rbind("drAL_CvA" = contrasts21(con_drAL_adhd * -1 + con_drAL_ctrl))
con_drAR_CvA <- rbind("drAR_CvA" = contrasts21(con_drAR_adhd * -1 + con_drAR_ctrl))

# "main effect" of task within ADHD
cat("TEST CONTRAST: NvLR_adhd", con_NvLR_adhd)
summary(glht(fa_contr, linfct = mcp(all_factors = con_NvLR_adhd)), test = Ftest())
cat("TEST CONTRAST: LvNR_adhd", con_LvNR_adhd)
summary(glht(fa_contr, linfct = mcp(all_factors = con_LvNR_adhd)), test = Ftest())
cat("TEST CONTRAST: RvNL_adhd", con_RvNL_adhd)
summary(glht(fa_contr, linfct = mcp(all_factors = con_RvNL_adhd)), test = Ftest())

# "main effect" of distractor within ADHD
cat("TEST CONTRAST: dstr_adhd", con_dstr_adhd)
summary(glht(fa_contr, linfct = mcp(all_factors = con_dstr_adhd)), test = Ftest())

# Interaction of distractor and task levels in ADHD
cat("TEST CONTRAST: drAN_adhd", con_drAN_adhd)
summary(glht(fa_contr, linfct = mcp(all_factors = con_drAN_adhd)), test = Ftest())
cat("TEST CONTRAST: drAL_adhd", con_drAL_adhd)
summary(glht(fa_contr, linfct = mcp(all_factors = con_drAL_adhd)), test = Ftest())
cat("TEST CONTRAST: drAR_adhd", con_drAR_adhd)
summary(glht(fa_contr, linfct = mcp(all_factors = con_drAR_adhd)), test = Ftest())

# "main effect" of task within CTRL
cat("TEST CONTRAST: NvLR_ctrl", con_NvLR_ctrl)
summary(glht(fa_contr, linfct = mcp(all_factors = con_NvLR_ctrl)), test = Ftest())
cat("TEST CONTRAST: LvNR_ctrl", con_LvNR_ctrl)
summary(glht(fa_contr, linfct = mcp(all_factors = con_LvNR_ctrl)), test = Ftest())
cat("TEST CONTRAST: RvNL_ctrl", con_RvNL_ctrl)
summary(glht(fa_contr, linfct = mcp(all_factors = con_RvNL_ctrl)), test = Ftest())

# "main effect" of distractor within CTRL
cat("TEST CONTRAST: dstr_ctrl", con_dstr_ctrl)
summary(glht(fa_contr, linfct = mcp(all_factors = con_dstr_ctrl)), test = Ftest())

# Interaction of distractor and task levels in CTRL
cat("TEST CONTRAST: drAN_ctrl", con_drAN_ctrl)
summary(glht(fa_contr, linfct = mcp(all_factors = con_drAN_ctrl)), test = Ftest())
cat("TEST CONTRAST: drAL_ctrl", con_drAL_ctrl)
summary(glht(fa_contr, linfct = mcp(all_factors = con_drAL_ctrl)), test = Ftest())
cat("TEST CONTRAST: drAR_ctrl", con_drAR_ctrl)
summary(glht(fa_contr, linfct = mcp(all_factors = con_drAR_ctrl)), test = Ftest())

# Interaction of distractor and task levels between ADHD & CTRL
cat("TEST CONTRAST: drAN_ctrl V ADHD", con_drAN_CvA)
summary(glht(fa_contr, linfct = mcp(all_factors = con_drAN_CvA)), test = Ftest())
cat("TEST CONTRAST: drAL_ctrl V ADHD", con_drAL_CvA)
summary(glht(fa_contr, linfct = mcp(all_factors = con_drAL_CvA)), test = Ftest())
cat("TEST CONTRAST: drAR_ctrl V ADHD", con_drAR_CvA)
summary(glht(fa_contr, linfct = mcp(all_factors = con_drAR_CvA)), test = Ftest())

```



## Distractor effect

```{r distractor_effect, warning = FALSE, fig.align = "center"}
if (PLOTS){
# Distractor effect, group level.
distractor_effect %>%
  ggplot(aes(x = Task, y = distractor_effect, linetype = Group, color = Group)) +
    geom_boxplot(outlier.alpha = 0, alpha = 1/5) +
    geom_point(position = position_jitterdodge(jitter.width = 0.2)) +
    # geom_half_violin(draw_quantiles = c(0.25, 0.5, 0.75), alpha = 0) +
    xlab("Task") +
    ylab("Distractor effect") +
    ggtitle("Distractor effect, all task conditions, group level") +
    get(plot_theme)()
if (SAVE)
  ggsave(file.path(odir, "DistractorEffect.svg"))

}
if (PLOTS){
# Distractor effect, group level, barchart with SEM.
p_dodge <- position_dodge(width = 0.9)

distractor_effect %>%
  group_by(Group, Task) %>%
  summarise(DE_mean = mean(distractor_effect),
            DE_sem = sd(distractor_effect)/sqrt(n())) %>%
  ggplot(aes(x = Task, y = DE_mean, fill = Group)) +
    geom_col(position = p_dodge) +
    geom_errorbar(aes(ymin = DE_mean - DE_sem, ymax = DE_mean + DE_sem),
                  position = p_dodge, width = 0.25) +
    xlab("Task") +
    ylab("Distractor effect") +
    ggtitle("Distractor effect, all task conditions, group level, +/- SEM") +
    scale_fill_brewer(palette = "Greys") +
    get(plot_theme)()

}
if (PLOTS){
# Distractor effect, single subject.
distractor_effect %>%
  ggplot(aes(x = Task, y = distractor_effect, color = dom_resp)) +
    geom_line(aes(group = ID)) +
    geom_point() +
    facet_wrap(~Group) +
    xlab("Task") +
    ylab("Distractor effect") +
    ggtitle("Distractor effect, all task conditions, single subject") +
    get(plot_theme)() +
    theme(legend.position = "none")
}
# # Does response hand counter-balancing in CONTROL group affect DE?
ks.test(filter(distractor_effect, Group == "Control" & !dom_resp)$distractor_effect,
         filter(distractor_effect, Group == "Control" & dom_resp)$distractor_effect)
```

### Statistics for distractor effect:

```{r distractor_effect_stats, warning = FALSE, fig.align = "center"}
# Mixed 2-way ANOVA.
de_stats <- ezANOVA(distractor_effect, dv = .(distractor_effect),
                    wid = .(ID),
                    within = .(Task),
                    between = .(Group),
                    type = 3, detailed = FALSE, return_aov = TRUE)
if (DIAGNOSTICS){
  ezanova_residuals <- purrr::map(de_stats$aov, residuals)
  ezanova_residuals_tbl <- enframe(ezanova_residuals) %>% unnest
  hist(ezanova_residuals_tbl$value)
  shapiro.test(ezanova_residuals_tbl$value)
  print(de_stats)
}

# distractor effect by lmer
de_lmer <- lmer(distractor_effect ~ Group*Task + (1|ID), data = distractor_effect)

distractor_effect$Group <- relevel(distractor_effect$Group, ref = "Control")
distractor_effect$all_factors <- with(distractor_effect, interaction(Group, Task))
levels(distractor_effect$all_factors)
de_contr <- lmer(distractor_effect ~ all_factors + (1|ID), data = distractor_effect)

```


### Contrasts for distractor effect:


```{r}
de.grid.lvls <- expand.grid(Task = c('AttendFull', 'AttendLeft', 'AttendRight'),
                            Group = c('ADHD', 'Control'))

cbind(de.grid.lvls, de = predict(de_lmer, newdata = de.grid.lvls, re.form=NA)) %>%
  ggplot(aes(Task, de, linetype=Group)) + geom_point() +
  geom_line(aes(group=Group),size=1) +
  theme_bw() + ggtitle("Distractor Effect") + ylab("Distractor Effect")

joint_tests(de_lmer)
joint_tests(de_lmer, by = "Group")
joint_tests(de_lmer, by = "Task")

# "main effect" of group
con_grp <- rbind("DE_group" = c(1,-1,1,-1,1,-1))
summary(glht(de_contr, linfct = mcp(all_factors = con_grp)), test = Ftest())

# # "main effect" of task within ADHD
con_FvLR_adhd <- rbind("FvLR_adhd" = c(0,1,0,-0.5,0,-0.5))
summary(glht(de_contr, linfct = mcp(all_factors = con_FvLR_adhd)), test = Ftest())
con_LvFR_adhd <- rbind("LvFR_adhd" = c(0,0.5,0,-1,0,0.5))
summary(glht(de_contr, linfct = mcp(all_factors = con_LvFR_adhd)), test = Ftest())
con_RvFL_adhd <- rbind("RvFL_adhd" = c(0,0.5,0,0.5,0,-1))
summary(glht(de_contr, linfct = mcp(all_factors = con_RvFL_adhd)), test = Ftest())

# "main effect" of task within CTRL
con_FvLR_ctrl <- rbind("FvLR_ctrl" = c(1,0,-0.5,0,-0.5,0))
summary(glht(de_contr, linfct = mcp(all_factors = con_FvLR_ctrl)), test = Ftest())
con_LvFR_ctrl <- rbind("LvFR_ctrl" = c(-0.5,0,1,0,-0.5,0))
summary(glht(de_contr, linfct = mcp(all_factors = con_LvFR_ctrl)), test = Ftest())
con_RvFL_ctrl <- rbind("RvFL_ctrl" = c(-0.5,0,-0.5,0,1,0))
summary(glht(de_contr, linfct = mcp(all_factors = con_RvFL_ctrl)), test = Ftest())

# interaction of group and task
con_F_CvA <- contrasts21(con_FvLR_adhd * -1 + con_FvLR_ctrl)
con_L_CvA <- contrasts21(con_LvFR_adhd * -1 + con_LvFR_ctrl)
con_R_CvA <- contrasts21(con_RvFL_adhd * -1 + con_RvFL_ctrl)

# Interaction of task levels and ADHD vs CTRL
cat("TEST CONTRAST: FvLR ctrl V ADHD", con_F_CvA)
summary(glht(de_contr, linfct = mcp(all_factors = con_F_CvA)), test = Ftest())
cat("TEST CONTRAST: LvFR ctrl V ADHD", con_L_CvA)
summary(glht(de_contr, linfct = mcp(all_factors = con_L_CvA)), test = Ftest())
cat("TEST CONTRAST: RvFL ctrl V ADHD", con_R_CvA)
summary(glht(de_contr, linfct = mcp(all_factors = con_R_CvA)), test = Ftest())
```

### DE summary

There was no effect of group on Distractor effect. Task = attend-Full differed strongly from Left/Right for CTRL group (F = 11), and this induced a between groups difference with ADHD in the same Task contrast (F = 4.2)